Deuteron Electro-Disintegration at Very High Missing Momenta

### 2020-06-26 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/MARKED_PRL/body.tex
updated

with a bin width of $\pm 5^{\circ}$. The data is compared to the previous Hall A experiment (red square) results \cite{PhysRevLett.107.262501} as well as the theoretical reduced cross sections using the Paris(blue),
AV18(green) and CD-Bonn(magenta) NN potentials.}

@@

cross sections using the charge-dependent Bonn (CD-Bonn) \cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18) \cite{PhysRevC.51.38} and Paris \cite{PhysRevC.21.861} NN-potentials. The theoretical calculations
for the CD-Bonn (magenta) and AV18 (green) potentials were performed by Sargsian \cite{PhysRevC.82.014612} within the GEA and those for the Paris potential (blue) were by Laget \cite{LAGET2005} within the diagrammatic approach.\\

@@

\indent Beyond $p_{\mathrm{r}}\sim250$ MeV/c at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the Paris and
AV18 models increasingly differ from the CD-Bonn calculation. In this region, the Paris/AV18 cross sections are dominated by the PWIA and in good agreement up to $p_{\mathrm{r}}\sim700$ MeV/c. The CD-Bonn cross sections in contrast are generally smaller than the Paris/AV18 in this region.  In addition, for $\theta_{nq}=35^{\circ}$, they are dominated by the PWIA up to $p_{\mathrm{r}}\sim800$ MeV/c (Fig. \hyperref[fig:fig1]{1(a)})  while for $\theta_{nq}=45^{\circ}$  FSI start to contribute already above 600 MeV/c (Fig. \hyperref[fig:fig1]{1(b)}).\\

@@

\indent Overall, it is interesting to note that none of the calculations can reproduce the measured $p_{\mathrm{r}}$ dependence above 600 MeV/c in a region where FSI are still relatively small $(<30\%)$.  This behavior of the data is new
and additional data in this kinematic region are necessary to improve the statistics. \\

@@

Furthermore, the CD-Bonn model was found to be significantly different than the Paris or AV18 models and was able to partially describe the data over a larger range in $p_{\mathrm{r}}$.

>>>>

with a bin width of $\pm 5^{\circ}$. The data is compared to the previous Hall A experiment (red square) results \cite{PhysRevLett.107.262501} as well as the theoretical reduced cross sections using the Paris (blue),
AV18 (green), CD-Bonn (magenta) and WJC2 (orange) NN potentials.}

@@

cross sections using the charge-dependent Bonn (CD-Bonn) \cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18) \cite{PhysRevC.51.38}, Paris \cite{PhysRevC.21.861} and WJC2 \cite{Gross_2007} NN potentials. The theoretical calculations
for the CD-Bonn (magenta) and AV18 (green) potentials were performed by Sargsian \cite{PhysRevC.82.014612} within the GEA and those for the Paris potential (blue) were by Laget \cite{LAGET2005} within the diagrammatic approach.
For the WJC2 (orange) potential, the calculations were done by Orden and Jeschonnek \cite{PhysRevC.90.064006} using a Bethe-Salpeter-like formalism for two-body bound states. The calculations
used two different form factor parametrizations (GKex05 \cite{PhysRevC.66.045501}, AMT \cite{PhysRevC.76.035205}) where a discrepancy of $\sim5.8-6.6 \%$ was found between the respective
WJC2 reduced cross sections. Figure \ref{fig:fig1} shows the results using only the WJC2 (GKex05) parametrization. \\

@@

\indent Beyond $p_{\mathrm{r}}\sim250$ MeV/c at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the Paris,
AV18 and WJC2 models increasingly differ from the CD-Bonn calculation. In this region, the Paris/AV18 cross sections are dominated by the PWIA and in good agreement up to $p_{\mathrm{r}}\sim700$ MeV/c whereas
the WJC2 PWIA falls off with a comparatively smaller cross section at $\theta_{nq}=35^{\circ}$. The CD-Bonn cross sections in contrast are generally smaller than the Paris, AV18 and WJC2 in this region.
In addition, for $\theta_{nq}=35^{\circ}$, they are dominated by the PWIA up to $p_{\mathrm{r}}\sim800$ MeV/c
(Fig. \hyperref[fig:fig1]{1(a)})  while for $\theta_{nq}=45^{\circ}$  FSI start to contribute already above 600 MeV/c (Fig. \hyperref[fig:fig1]{1(b)}).\\
\indent Moreover, in spite of the partial agreement between data and theory, between $p_{\mathrm{r}} \sim 0.55$ and 1.0 GeV/c, all models exhibit a
steeper fall-off compared to data. This discrepancy was quantified by doing a linear fit to the data and each of the PWIA calculations. A difference of at least
4.241 standard deviations was found between the data and theory slopes which corresponds to a probability $\leq 1.1\times 10^{-5}$ (very unlikely) that the observed discrepancy is due to a statistical fluctuation. \\ 

@@

\indent Overall, it is interesting to note that none of the calculations can reproduce the measured $p_{\mathrm{r}}$ dependence above 600 MeV/c in a
region where FSI are still relatively small $(<30\%)$. This behavior of the data is new and additional data in this kinematic region are necessary
to improve the statistics. \\

@@

Furthermore, the CD-Bonn model was found to be significantly different than the Paris, AV18 or WJC2 models and was able to partially describe the data over a larger range in $p_{\mathrm{r}}$.

### 2020-06-26 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/MARKED_PRL/latexdiff/body.tex
updated

\includegraphics[scale=0.46]{prl_plots/PRL_plot1.pdf}

@@

cross sections using the charge-dependent Bonn (CD-Bonn) \cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18) \cite{PhysRevC.51.38} and Paris \cite{PhysRevC.21.861} NN-potentials. The theoretical calculations
for the CD-Bonn (magenta) and AV18 (green) potentials were performed by Sargsian \cite{PhysRevC.82.014612} within the GEA and those for the Paris potential (blue) were by Laget \cite{LAGET2005} within the diagrammatic approach.\\
\indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{\mathrm{r}}\leq300$ MeV/c, the cross sections are well reproduced  by  all models when FSI are included.

@@

\indent Beyond $p_{\mathrm{r}}\sim250$ MeV/c at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the Paris and
AV18 models increasingly differ from the CD-Bonn. In this region, the Paris/AV18 cross sections are dominated by the PWIA and in good agreement up to $p_{\mathrm{r}}\sim700$ MeV/c. The CD-Bonn cross sections in contrast are generally smaller than the Paris/AV18 in this region.  In addition, for $\theta_{nq}=35^{\circ}$, they are dominated by the PWIA up to $p_{\mathrm{r}}\sim800$ MeV/c (Fig. \hyperref[fig:fig1]{1(a)})  while for $\theta_{nq}=45^{\circ}$  FSI start to contribute already above 600 MeV/c (Fig. \hyperref[fig:fig1]{1(b)}).\\

@@

nucleon-neson-meson couplings are constrained to describe the NN scattering phase shifts

@@

results in a less high momentum component in the deuteron wave function in the momentum space.

@@

\includegraphics[scale=0.5]{./prl_plots/PRL_plot2.pdf}

@@

Furthermore, the CD-Bonn model was found to be significantly different than the Paris or AV18 models and was able to partially describe the data over a larger range in $p_{\mathrm{r}}$.
At higher missing momenta ($p_{\mathrm{r}}>700$ MeV/c), however, all models were unable to describe the data. \\
\indent In conclusion, additional measurements of the $^{2}\mathrm{H}(e,e'p)n$ would be required to reduce the statistical uncertainties in this very high missing
momentum region ($p_{\mathrm{r}}>500$ MeV/c) to better understand the large deviations observed between the different models and data.

>>>>

\includegraphics[scale=0.46]{prl_plots/PRL_plot1_WJC2.pdf}

@@

cross sections using the charge-dependent Bonn (CD-Bonn) \cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18) \cite{PhysRevC.51.38}, Paris \cite{PhysRevC.21.861} and WJC2 \cite{Gross_2007} NN potentials. The theoretical calculations
for the CD-Bonn (magenta) and AV18 (green) potentials were performed by Sargsian \cite{PhysRevC.82.014612} within the GEA and those for the Paris potential (blue) were by Laget \cite{LAGET2005} within the diagrammatic approach.
For the WJC2 (orange) potential, the calculations were done by Orden and Jeschonnek \cite{PhysRevC.90.064006} using a Bethe-Salpeter-like formalism for two-body bound states. The calculations
used two different form factor parametrizations (GKex05 \cite{PhysRevC.66.045501}, AMT \cite{PhysRevC.76.035205}) where a discrepancy of $\sim5.8-6.6 \%$ was found between the respective
WJC2 reduced cross sections. Figure \ref{fig:fig1} shows the results using only the WJC2 (GKex05) parametrization. \\
\indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{\mathrm{r}}\leq250$ MeV/c, the cross sections are well reproduced by all models when FSI are included.

@@

\indent Beyond $p_{\mathrm{r}}\sim250$ MeV/c at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the Paris,
AV18 and WJC2 models increasingly differ from the CD-Bonn calculation. In this region, the Paris/AV18 cross sections are dominated by the PWIA and in good agreement up to $p_{\mathrm{r}}\sim700$ MeV/c whereas
the WJC2 PWIA falls off with a comparatively smaller cross section at $\theta_{nq}=35^{\circ}$. The CD-Bonn cross sections in contrast are generally smaller than the Paris, AV18 and WJC2 in this region.
In addition, for $\theta_{nq}=35^{\circ}$, they are dominated by the PWIA up to $p_{\mathrm{r}}\sim800$ MeV/c
(Fig. \hyperref[fig:fig1]{1(a)})  while for $\theta_{nq}=45^{\circ}$  FSI start to contribute already above 600 MeV/c (Fig. \hyperref[fig:fig1]{1(b)}).\\
\indent Moreover, in spite of the partial agreement between data and theory, at $p_{\mathrm{r}} \sim 0.55-1.0$ GeV/c, the data exhibits a smaller
fall-off compared to all models which was quantified by a linear fit to both the data and each of the PWIA calculations. A difference of at least
4.241 standard deviations was found which corresponds to a probability of $1.1\times 10^{-5}$ (very unlikely) that the observed discrepancy is due to a statistical fluctuation. \\ 

@@

nucleon-meson-meson couplings are constrained to describe the NN scattering phase shifts

@@

results in a smaller high momentum component in the deuteron wave function in momentum space.

@@

\includegraphics[scale=0.5]{./prl_plots/PRL_plot2_WJC2.pdf}

@@

Furthermore, the CD-Bonn model was found to be significantly different than the Paris, AV18 or WJC2 models and was able to partially describe the data over a larger range in $p_{\mathrm{r}}$.
At higher missing momenta ($p_{\mathrm{r}}>700$ MeV/c), however, all models were unable to describe the data. 
Additional measurements of the $^{2}\mathrm{H}(e,e'p)n$ would be required to reduce the statistical uncertainties in this very high missing
momentum region ($p_{\mathrm{r}}>500$ MeV/c) to better understand the large deviations observed between the different models and data.\\
